---
title: "Fishery Data Summary - Sablefish"
#author: "Cindy Tribuzio"
#date: "8/10/2021"
output: 
  bookdown::word_document2:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
# Setup ----
libs <- c("plyr","tidyverse","ggplot2","patchwork","flextable","bookdown","knitr", "lubridate","janitor")
if(length(libs[which(libs %in% rownames(installed.packages()) == FALSE )]) > 0) {
  install.packages(libs[which(libs %in% rownames(installed.packages()) == FALSE)])}
lapply(libs, library, character.only = TRUE)


datadir<-(paste(getwd(),"/Data/",sep=""))
outdir<-(paste(getwd(),"/Output/",sep=""))

theme_SAFE<-function(x){
  big_border <- fp_border(width = 2)
  std_border <- fp_border(width = 1)
  x<-fontsize(x,size=10,part="all")
  x<-font(x,fontname="Times New Roman",part="all")
  x<-bold(x,part="header")
  x <- hline_top(x, border = big_border, part = "header")
  x <- hline(x, border = std_border, part = "header")
  x <- hline_bottom(x, border = big_border, part = "body")
  x <- align(x,align="center",part="header")
}

'%nin%'<-Negate('%in%')
```
# Introduction
This report summarizes the fishery depenent data that are available and inform the Gulf of Alaska (GOA) and Bering Sea/Aleutian Islands (BSAI) sablefish stock assessment. 

NOTES: 

1) These data are preliminary and should not be considered absolute. The logic used in linking trips with observer information is still being solidified and there are some issues still to be resolved by AKRO and FMA.

2) Numbers may not exactly match those in annual report due to differences in observer strata assignments from what vessels log into the deployment system compared to what is reported on the fish tickets. Overall, differences are expected to be minor.

3) Starts in 2013 because sampling strata is limited to "old program" prior to that. Not helpful.

## Observer Deployment Performance
This section summarizes the projected and realized observer coverage rates since 2016 for patial coverage trips. Values are from the Annual Deployment Plans and the Annual Reports, available on the NPFMC website. Full coverage trips are all assumed to be 100% covered. Zero selection is also not included. Not all observer strata were covered each year. For example, Hook-and-line (HAL) tender was only covered in 2017, in which a total of four trips were made and thus deemed not a useful strata to include. In 2020, observer sampling was significantly impacted March-June due to the pandemic, resulting in minimal coverage during those months and reducing the annual realized coverage rates. The trawl EM EFP went into effect in 2020, in this strata all trips are 100% reviewed, however, the shoreside offloads are 30% reviewed in the GOA and 100% reviewed in the BSAI. The below table only documents partial coverage rates.
```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
obs_cov_dat <- read_csv(paste(datadir,"OBS_rates.csv",sep=""))
obs2 <- obs_cov_dat %>% 
  mutate(colvals = paste(format(Expected, drop0trailing = F),"%(",format(Actual,drop0trailing = F),"%)",sep="")) %>%
  select(Year, Strata, colvals) %>% 
  filter(Strata != "No Selection") %>% 
  spread(Strata, colvals)
obstab <- flextable(obs2,
                    col_keys = colnames(obs2),
                    theme_fun = theme_SAFE) %>% 
  align(j=c("Year"),align = "Center",part="body") %>% 
  colformat_num(j=c("Year"),big.mark = "",digits=0)

```
```{r, echo=F}
kable(obs2, caption = "Expected observer coverage rate (from the Annual Deployment plans) and realized observer coverage rate (from the Annual Reviews, table 5 or 3.5 depending on version)")

```
## Total Catch
```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
CAS_dat<-read.csv(paste(datadir,"gfcatchbyfishery_withnewfields_sablefish.csv",sep=""), header=T)
head(CAS_dat)
CAS_dat <- CAS_dat %>% 
  filter(FMP_SUBAREA %nin% c("SEI","PWSI")) %>% 
  filter(YEAR >2012) %>%
  mutate(WEEK_ENDING_DATE = ymd(WEEK_ENDING_DATE),
         mgmt_area = if_else(FMP_SUBAREA == "BS", "BS",
                             if_else(FMP_SUBAREA == "AI", "AI",
                                     if_else(FMP_SUBAREA == "WG", "WGOA",
                                             if_else(FMP_SUBAREA == "CG", "CGOA", "EGOA")))),
         OBS_Coverage = if_else(GEAR == "HAL" & SAMPLING_STRATA_NAME == "No Selection", "HAL-None",
                                if_else(GEAR == "HAL" & SAMPLING_STRATA_NAME == "Full Selection", "HAL-Human-Full",
                                        if_else(GEAR == "HAL" & SAMPLING_STRATA_NAME == "EM Hook-and-Line Trip Selection", "HAL-EM-Partial",
                                                if_else(GEAR == "HAL" & SAMPLING_STRATA_NAME == "Vessel Selection"|
                                                          GEAR == "HAL" & SAMPLING_STRATA_NAME == "Trip Selection"|
                                                          GEAR == "HAL" & SAMPLING_STRATA_NAME == "Hook-and-Line Trip Selection"|
                                                          GEAR == "HAL" & SAMPLING_STRATA_NAME == "Small-Vessel Trip Selection"|
                                                          GEAR == "HAL" & SAMPLING_STRATA_NAME == "Large-Vessel Trip Selection","HAL-Human-Partial",
                                                        if_else(GEAR == "NPT" & SAMPLING_STRATA_NAME == "No Selection"|
                                                                  GEAR == "PTR" & SAMPLING_STRATA_NAME == "No Selection", "Trawl-None",
                                                                if_else(GEAR == "NPT" & SAMPLING_STRATA_NAME == "Full Selection"|
                                                                          GEAR == "PTR" & SAMPLING_STRATA_NAME == "Full Selection", "Trawl-Human-Full",
                                                                        if_else(GEAR == "NPT" & SAMPLING_STRATA_NAME == "EM Trawl Selection"|
                                                                                  GEAR == "PTR" & SAMPLING_STRATA_NAME == "EM Trawl Selection",
                                                                                "Trawl-EM-Partial",
                                                                                if_else(GEAR == "NPT" & SAMPLING_STRATA_NAME == "Vessel Selection"|
                                                                                          GEAR == "NPT" & SAMPLING_STRATA_NAME == "Trip Selection"|
                                                                                          GEAR == "NPT" & SAMPLING_STRATA_NAME == "Trawl Trip Selection"|
                                                                                          GEAR == "NPT" & SAMPLING_STRATA_NAME == "Small-Vessel Trip Selection"|
                                                                                          GEAR == "NPT" & SAMPLING_STRATA_NAME == "Large-Vessel Trip Selection"|
                                                                                          GEAR == "PTR" & SAMPLING_STRATA_NAME == "Vessel Selection"|
                                                                                          GEAR == "PTR" & SAMPLING_STRATA_NAME == "Trip Selection"|
                                                                                          GEAR == "PTR" & SAMPLING_STRATA_NAME == "Trawl Trip Selection"|
                                                                                          GEAR == "PTR" & SAMPLING_STRATA_NAME == "Small-Vessel Trip Selection"|
                                                                                          GEAR == "PTR" & SAMPLING_STRATA_NAME == "Large-Vessel Trip Selection",
                                                                                        "Trawl-Human-Partial",
                                                                                        if_else(GEAR == "NPT" & SAMPLING_STRATA_NAME == "Tender Trawl Trip Selection"|
                                                                                                  GEAR == "PTR" & SAMPLING_STRATA_NAME == "Tender Trawl Trip Selection",
                                                                                                "Trawl-Tender-Human-Partial",
                                                                                                if_else(GEAR == "PTR" & SAMPLING_STRATA_NAME == "Trawl EM Parital Coverage Selection", "Trawl-EM-Partial",
                                                                                                        if_else(GEAR == "PTR" & SAMPLING_STRATA_NAME == "Trawl EM Full Coverage Selection", "Trawl-EM-Full",
                                                                                                                if_else(GEAR == "JIG", "Jig-None",
                                                                                                                        if_else(GEAR == "POT" & SAMPLING_STRATA_NAME == "No Selection", "Pot-None",
                                                                                                                                if_else(GEAR == "POT" & SAMPLING_STRATA_NAME == "Full Selection", "Pot-Human-Full",
                                                                                                                                        if_else(GEAR == "POT" & SAMPLING_STRATA_NAME == "EM Pot Trip Selection", "Pot-EM-Partial",
                                                                                                                                                if_else(GEAR == "POT" & SAMPLING_STRATA_NAME == "EM Pot Tender Trip Selection", "Pot-Tender-EM-Partial",
                                                                                                                                                        if_else(GEAR == "POT" & SAMPLING_STRATA_NAME == "Tender Pot Trip Selection", "Pot-Tender-Human-Partial","Pot-Human-Partial"))))))))))))))))))

#broke it into two steps because the above code was soooooooo long
CAS_dat <- CAS_dat %>% 
  mutate(observed = if_else(MONITORING_STATUS == "FIXED_GEAR_EM", "Catch",
                             if_else(MONITORING_STATUS == "TRAWL_EM" | 
                                       MONITORING_STATUS == "NO_MONITORING", "None","Catch/Biologicals")))
                                                                                                              
levels <- CAS_dat %>% 
  select(GEAR, SAMPLING_STRATA_NAME, OBS_Coverage) %>% 
  unique() %>% 
  arrange(OBS_Coverage,GEAR)

area_catch <- CAS_dat %>% 
  group_by(YEAR, mgmt_area, GEAR) %>% 
  summarize(Catch_MT = sum(CATCH_MT))

area_catch$mgmt_area <- factor(area_catch$mgmt_area, 
                               levels = c("AI", "BS", "WGOA", "CGOA", "EGOA"))
fig1 <- ggplot(area_catch, aes(x=YEAR, y=Catch_MT, fill = GEAR, color = GEAR))+
  geom_bar(position = position_stack(), stat = "identity")+
  facet_grid(mgmt_area~.)
```
```{r totcatch, echo = FALSE, fig.cap = "Total catch estimates (mt) of sablefish in each management area. Colors represent the different gear types."}
fig1
```
```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
area_tot <- CAS_dat %>% 
  group_by(YEAR, mgmt_area) %>% 
  summarize(totcatch = sum(CATCH_MT))
obs_catch <- CAS_dat %>% 
  group_by(YEAR, mgmt_area, OBS_Coverage) %>% 
  summarize(Catch_MT = sum(CATCH_MT)) %>% 
  inner_join(area_tot, by = c("YEAR", "mgmt_area")) %>% 
  mutate(prop_catch = Catch_MT/totcatch)

fig2 <- ggplot(obs_catch, aes(x=YEAR, y=prop_catch, fill=OBS_Coverage, color=OBS_Coverage))+
  geom_bar(position = position_stack(), stat = "identity")+
  facet_grid(mgmt_area~.)
```
```{r fig2, echo = FALSE, fig.cap = "Proportion of total catch (mt) of sablefish in each management area by observer coverage type."}
fig2
```
```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
areagear_tot <- CAS_dat %>% 
  group_by(YEAR, mgmt_area, GEAR) %>% 
  summarize(totcatch = sum(CATCH_MT))

obs_prop <- CAS_dat %>% 
  group_by(YEAR, mgmt_area, observed, GEAR) %>% 
  summarize(Catch_MT = sum(CATCH_MT)) %>% 
  inner_join(areagear_tot, by = c("YEAR", "mgmt_area","GEAR")) %>% 
  mutate(prop_catch = Catch_MT/totcatch) %>% 
  filter(GEAR != "JIG")

fig3 <- ggplot(obs_prop, aes(x=YEAR, y=prop_catch, fill=observed, color=observed))+
  geom_bar(position = position_stack(), stat = "identity")+
  facet_grid(mgmt_area~GEAR)  
```
```{r fig3, echo = FALSE, fig.cap = "Proportion of total catch of sablefish that is observed in each management area and gear type. Catch is for fixed-gear EM, where only the catch is observed, but there is no biological sampling."}
fig3
```

## IFQ Catch
```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
CAS_dat <- CAS_dat %>% 
  mutate(IFQ = if_else(IFQSABL_CVTRIP_FLAG == "Y" |IFQSABL_CPTRIP_FLAG == "Y", "Y", "N"))

area_catch_IFQ <- CAS_dat %>% 
  group_by(YEAR, mgmt_area, IFQ) %>% 
  summarize(Catch_MT = sum(CATCH_MT)) %>% 
  inner_join(area_tot, by = c("YEAR", "mgmt_area")) %>% 
  mutate(prop_IFQ = Catch_MT/totcatch) %>% 
  select(-totcatch)  
  #pivot_longer(cols = c(Catch_MT, prop_IFQ), names_to = "Metric", values_to = "Catch")

area_catch_IFQ$mgmt_area <- factor(area_catch_IFQ$mgmt_area, 
                               levels = c("AI", "BS", "WGOA", "CGOA", "EGOA"))

fig4catch <- ggplot(area_catch_IFQ, aes(x=YEAR, y=Catch_MT, fill = IFQ, color = IFQ))+
  geom_bar(position = position_stack(), stat = "identity", show.legend = F)+
  facet_grid(mgmt_area~., scales = "free")
fig4prop <- ggplot(area_catch_IFQ, aes(x=YEAR, y=prop_IFQ, fill = IFQ, color = IFQ))+
  geom_bar(position = position_stack(), stat = "identity", show.legend = F)+
  facet_grid(mgmt_area~., scales = "free")
```
```{r fig4, echo=F, fig.cap = "Total and proportion of sablefish catch occuring in the IFQ fisheries. Red is non-IFQ and blue is IFQ."}
fig4catch+fig4prop
```
```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
area_tot_IFQ <- CAS_dat %>% 
  filter(IFQ == "Y") %>% 
  group_by(YEAR, mgmt_area) %>% 
  summarize(totcatch = sum(CATCH_MT))

IFQ_gear <- CAS_dat %>% 
  filter(IFQ == "Y") %>% 
  group_by(YEAR, mgmt_area, GEAR, IFQ) %>% 
  summarize(Catch = sum(CATCH_MT)) %>% 
  inner_join(area_tot_IFQ, by = c("YEAR", "mgmt_area")) %>% 
  mutate(prop_catch = Catch/totcatch)

IFQ_gear$mgmt_area <- factor(IFQ_gear$mgmt_area, 
                               levels = c("AI", "BS", "WGOA", "CGOA", "EGOA"))
fig5catch <- ggplot(IFQ_gear,aes(x=YEAR,y=Catch, fill = GEAR, color = GEAR))+
  geom_bar(position = position_stack(), stat = "identity", show.legend = F)+
  facet_grid(mgmt_area~.)
fig5prop <- ggplot(IFQ_gear,aes(x=YEAR,y=prop_catch, fill = GEAR, color = GEAR))+
  geom_bar(position = position_stack(), stat = "identity", show.legend = F)+
  facet_grid(mgmt_area~.)
```
```{r fig5, echo=F, fig.cap = "Total and proportion of sablefish IFQ catch by gear type. Red is hook-and-line, blue is pot."}
fig5catch+fig5prop
```

## Biologicals
The same preliminary data caveats apply to biological samples as well. 

Biological samples are collected either by an at-sea observer or port-sampled. The below can be broken out by port or at-sea collections to relfect the difference in spatial resolution of the data.

```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
# Get biological data ----
biodat<-read.csv(paste(datadir,"norpac_age_report_flattened_sablefish.csv",sep=""),header=T, skip=7)

#note differences in column heading styles.....grrrrr
#add week number to match above, it's not going to be a perfect match, but haul offload date is not likely to match week end date.
biodat$Haul.Offload.Date<-dmy(biodat$Haul.Offload.Date)
biodat$WEEK_ENDING_DATE<-ceiling_date(biodat$Haul.Offload.Date,"week")+
  ifelse(weekdays(biodat$Haul.Offload.Date) %in% c("Sunday"),6,-1)
biodat <- biodat %>% 
  filter(Year >= 2013, FMP.Area != "INSD") %>% 
  rename(YEAR = Year, VESSEL_FEDERAL_PERMIT = Permit)

#biodat$WEEK_NUMBER<-week(biodat$Haul.Offload.Date)

#drop uneeded fields for now
bd<-biodat[,c("T.Table","YEAR","WEEK_ENDING_DATE","VESSEL_FEDERAL_PERMIT","Vessel","Gear.Description","FMP.Area","FMP.Subarea","NMFS.Area",
              "Type.1.Otolith","Type.3.Sex.Length.Weight","Length..cm.","Weight..kg.","Age")]

# Merge ----
#trip info with biological based on year, week and federal permit
#need to run it separately based on offload sampling or observer sampling

#make matchable permit fields
#when T.Table==ATL_Haul Permit = VESSEL_FEDERAL_PERMIT
#when T.Table==ATL_oFFLOAD Permit = PROCESSOR_FEDERAL_PERMIT

#at-sea obs samples first
OBS<-bd[bd$T.Table=="ATL_HAUL",]

OBS2 <- OBS %>% 
  left_join(CAS_dat, by=c("YEAR","WEEK_ENDING_DATE","VESSEL_FEDERAL_PERMIT"))
OBS2<-OBS2[,!(names(OBS2) %in% c("VESSEL_FEDERAL_PERMIT"))]

#port obs samples second
PORT<-bd[bd$T.Table=="ATL_OFFLOAD",]
PORT2 <- PORT %>% 
  left_join(CAS_dat, by=c("YEAR","WEEK_ENDING_DATE","VESSEL_FEDERAL_PERMIT"))
PORT2<-PORT2[,!(names(PORT2) %in% c("VESSEL_FEDERAL_PERMIT"))]
#combine
bio_obs<-rbind(OBS2,PORT2)
bio_obs$FMP.Subarea <- factor(bio_obs$FMP.Subarea, 
                                levels = c("AI","BS","WG","CG","WY","SE"))
#write.csv(bio_obs,paste(cleandatdir,"biosampls_w_obs_sablefish.csv",sep=""),row.names = F)

bio_obs<-bio_obs[!is.na(bio_obs$SAMPLING_STRATA_NAME),]

#NOTE: still need to track down the ones that don't match up
bio_obs_nodat<-bio_obs[is.na(bio_obs$SAMPLING_STRATA_NAME),]

# Summary Figs ----
# LENGTHS ONLY ----
#coverage group of samples since 2013
ldat<-bio_obs[bio_obs$Type.3.Sex.Length.Weight=="Y",]
ct_l <- bio_obs %>% 
  clean_names() %>% 
  group_by(year, obs_coverage, fmp_subarea) %>% 
  summarise(n_samps = length(length_cm))
fig6_Lprop <- ggplot(ct_l,aes(x=year,y=n_samps,fill=obs_coverage))+
  geom_bar(position="fill", stat="identity")+
  labs(y="Proportion",title="Proportion Lengths")+
  facet_grid(fmp_subarea~.)

fig6_Lnum <-ggplot(ct_l,aes(x=year,y=n_samps,fill=obs_coverage))+
  geom_bar(position="stack", stat="identity", show.legend = F)+
  labs(y="n lengths",title="Sampled Lengths")+
  facet_grid(fmp_subarea~.)
```
```{r fig6, echo=F, fig.cap = "Total and proportion of lengths by observer strata in each management area"}
fig6_Lnum+fig6_Lprop
```
```{r, echo = FALSE, warning = FALSE, results = 'hide',include=FALSE}
Lrate <- bio_obs %>% 
  clean_names() %>% 
  group_by(year, obs_coverage, fmp_subarea) %>% 
  summarise(n_samps = length(length_cm), 
            catch = mean(catch_mt),
            Lratio = n_samps/catch)

fig7 <-ggplot(Lrate,aes(x=year,y=Lratio,fill=obs_coverage))+
  geom_bar(position="stack", stat="identity")+
  labs(y="n lengths/mt",title="Lengths per metric ton")+
  facet_grid(fmp_subarea~.)
```
```{r fig7, echo=F, fig.cap = "Ratio of number of lengths sampled to metric tons of catch by management area and observer strata"}
fig7
```


